SHAPR II: Dark Matter Substrcture? Beware the Effect of Edge-on Disks

### 2015-08-21 papers/B1555_EdgeOn/B1555_letter.tex
update to title and table

\title[Beware the Effect of Edge-on Disks]{
%Gravitational Lens Modelling of flux-ratio Anomalous System B1555+375
SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio
Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
Disks
}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

%\begin{table*}
\begin{table}
\centering
 %\begin{minipage}{140mm}
  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec). Uncertainties in position measurements are $0.001^ {\prime \prime}$ expect image D with larger uncertainty ($0.006^ {\prime \prime}$).}
  \begin{tabular}{@{}ccccc}
\hline

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{2}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} 	\\
					 &East &North &East 		&North \\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
B ........ &$-0.0726$ 	&$+0.0480 $	&$-0.0727$ &$+0.0477$  \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0281$   \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1630$ &$-0.3653$  \\  
%A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
%B ........ &$-0.0726\pm 0.001$ 	&$+0.0480 \pm 0.001$	&$-0.0727$ &$+0.0477$  \\  
%C ........ &$-0.4117\pm 0.001$  &$-0.0280 \pm 0.001$	&$-0.4117$ &$-0.0281$   \\  
%D ........ &$-0.1619\pm 0.006$  &$-0.3680\pm 0.006$	&$-0.1630$ &$-0.3653$  \\  
\hline
\end{tabular}

%\end{minipage}
%\medskip
\end{table}
%\end{table*}

@@

\begin{table}
 \centering
% \begin{minipage}{140mm}
  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios from SIE-only and SIE+expdisk model.}
  \begin{tabular}{@{}ccccccc}

\hline
	& MERLIN  & \multicolumn{2}{c}{Model}\\
		&5 GHz   & SIE-only & SIE+expdisk \\
\hline
$f_A/f_B$			&$1.61 \pm 0.10$ &$1.04$& $1.62$  \\ 
$f_A/f_C$		&$1.97 \pm 0.12$ 	 &$3.20$ & $2.17$ \\
$f_A/f_D$		&$11.62 \pm 3.24 $  &$9.67$& $8.69$ \\

\hline
\end{tabular}

%\end{minipage}
\medskip
\end{table}

>>>>

\title[Beware the Effect of Edge-on Disks]{
%Gravitational Lens Modelling of flux-ratio Anomalous System B1555+375
%SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio
%Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
%Disks
SHAPR II: Dark Matter Substrcture? Beware the Effect of Edge-on Disks
}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

\begin{table*}
%\begin{table}
\centering
 \begin{minipage}{140mm}
  \caption{Observation and lens model-predicted results summary. Radio lensed image positions \citep{Marlow99} (in arcsec) and flux ratios \citep{K03} are respect to image A. Uncertainties in position measurements are $0.001^ {\prime \prime}$ expect image D with larger uncertainty ($0.006^ {\prime \prime}$). }
  \begin{tabular}{@{}cccccccc}
\hline

Component	&\multicolumn{3}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model-Predicted} \\
					&\multicolumn{3}{c}{5 GHz}		&	\multicolumn{3}{c}{SIE+expdisk} & SIE-only 	\\
					 &East &North & Flux Ratio &East 		&North & Flux Ratio &Flux Ratio \\ 
\hline
A ........ &$0$    		&$0$		&   $1$ &$0.0000$ &$0.0000$ &  $1$ & $1$\\  
B ........ &$-0.0726$ 	&$+0.0480 $	& $0.620 \pm 0.039 $  &$-0.0727$ &$+0.0477$ & $0.620$ & $0.962 $ \\  
C ........ &$-0.4117$  &$-0.0280$	& $0.507\pm 0.030$ &$-0.4117$ &$-0.0281$   & $ 0.461 $ & $0.313 $\\  
D ........ &$-0.1619$  &$-0.3680$	& $0.086 \pm 0.024$  &$-0.1630$ &$-0.3653$  & $0.115$ & $0.103 $\\  
%A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
%B ........ &$-0.0726\pm 0.001$ 	&$+0.0480 \pm 0.001$	&$-0.0727$ &$+0.0477$  \\  
%C ........ &$-0.4117\pm 0.001$  &$-0.0280 \pm 0.001$	&$-0.4117$ &$-0.0281$   \\  
%D ........ &$-0.1619\pm 0.006$  &$-0.3680\pm 0.006$	&$-0.1630$ &$-0.3653$  \\  
\hline
\end{tabular}

\end{minipage}
%\medskip
%\end{table}
\end{table*}

@@

%\begin{table}
% \centering
% \begin{minipage}{140mm}
%  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios from SIE-only and SIE+expdisk model.}
%  \begin{tabular}{@{}ccccccc}

%\hline
%	& MERLIN  & \multicolumn{2}{c}{Model}\\
%		&5 GHz   & SIE-only & SIE+expdisk \\
%\hline
%$f_A/f_B$			&$1.61 \pm 0.10$ &$1.04$& $1.62$  \\ 
%$f_A/f_C$		&$1.97 \pm 0.12$ 	 &$3.20$ & $2.17$ \\
%$f_A/f_D$		&$11.62 \pm 3.24 $  &$9.67$& $8.69$ \\
